Embedding Intuitionistic into Classical Logic

### 2022-07-15 CSL/lipics-v2021-EIICL.tex
Space

\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{arrows,shapes,quotes}

@@

\begin{theorem}
	Let $\mathcal S$ be as above. Let $\mathcal F_\to\subseteq\mathcal S$ denote formulas $\psi$ of the form $(A_\psi\to B_\psi)\to C_\psi$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including formulas as follows
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore there is an effective procedure for translating counter-models between the sentences.
\end{theorem}

@@

\begin{theorem}
	For every predicate formula $\varphi$ there exists an effective procedure that yields an atom $P$ and a set $\mathcal S$ of formulas of the forms
	$$\forall \vec z(A(\vec a)\to (B(\vec b)\wedge C(\vec c))), \forall \vec z((A(\vec a)\wedge B(\vec b))\to C(\vec c)),$$$$\forall \vec z(A(\vec a)\to (B(\vec b)\vee C(\vec c))),
	\forall \vec z((A(\vec a)\vee B(\vec b))\to C(\vec c)),$$$$ \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c)),\forall \vec z(\forall xA(\vec a)\to B(\vec b)),$$$$ \forall \vec z(A(\vec a)\to\forall xB(b)), \forall \vec z(\exists xA(\vec a)\to B(\vec b)), \forall \vec z(A(\vec a)\to\exists xB(b))$$for atomic $A, B, C$ and vectors of variables $\vec z, \vec a, \vec b, \vec c$ such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The size of $\mathcal S$ and time complexity of the transformation are linear in the input size.
\end{theorem}

@@

\begin{definition}
A \emph{valuation} $v$ maps each propositional variable $A$ to a \emph{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$
		\item $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
A valuation $v$ is a \emph{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC} (Classical Propositional Calculus).
\end{definition}

@@

\begin{definition}
Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
		m, &\text{if $b=a$,}\\
		v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$.
		\item $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$.
		\item $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{M}$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$. A formula is valid if every $\Sigma$-structure satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, its (Kripke) \emph{Frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
	\begin{itemize}
		\item $M_u\subseteq M_w$.
		\item $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
		\item $R^{I_w}|_{M_u} = R^{I_u}$.
	\end{itemize}
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$
		\item $u, v\models R(t_1,\dots,t_n)$ iff $\mathcal M_u, v\models R(t_1,\dots,t_n)$.
		\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
		\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. A formula is valid if it is satisfied in eveery $\Sigma$-Kripke structure, it is valid for some Frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that Frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.
Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

\begin{example}
	Consider the law of excluded middle $$\varphi = (A\to \bot)\vee A$$ which is not intuitionistically valid. Then,
	\begin{align*}
		\varphi^{C} &= K(\varphi)\to ((A\to \bot)\vee A)^u\\
		&= K(\varphi)\to (A\to \bot)^u\vee A^u\\
		&= K(\varphi)\to (\forall u'( u\preceq u' \to A^{u'}\to \bot^{u'})\vee A(u))\\
		&= K(\varphi)\to (\forall u' (u\preceq u' \to A(u')\to \bot)\vee A(u)),
	\end{align*}
and indeed $\varphi^{C}$ admits a counter model with domain $\{u, u'\}$ where $u \preceq u'$, $A(u) = 0, A(u') = 1$.
\end{example}

@@

\begin{lemma}The following are true for both classical and intuitionistic semantics:
	\begin{itemize}
		\item $\bigwedge S^+(\varphi)\wedge P_\varphi\models\varphi$.
		\item $\bigwedge S^-(\varphi)\wedge \varphi\models P_\varphi$.
	\end{itemize}
\end{lemma}

\begin{proof}
The claims are verified in a straightforward manner by induction on $\varphi$.
\end{proof}

\begin{example}
	Consider $\varphi = \neg\forall x A(x)\to \exists x\neg A(x)$. Then
	\begin{align*}
		\mathcal S^+(\varphi) = &\{(P_\varphi\wedge P_{\neg\forall x A(x)})\to P_{\exists x\neg A(x)}, (P_{\forall xA(x)}\to\bot)\to P_{\neg \forall xA(x)}\}\\&\cup\{\forall xP_{A(x)}(x)\to P_{\forall xA(x)}, \forall x(P_{A(x)}(x)\to A(x))\}\\&\cup\{P_{\exists x\neg A(x)}\to \exists xP_{\neg A(x)}(x), \forall x(P_{\neg A(x)}(x)\to P_{A(x)}(x)\to \bot)\}\\&\cup\{\forall x(A(x)\to P_{A(a)}(x))\}\\
		\mathcal S^-(\varphi) = &\{(P_{\neg\forall x A(x)}\to P_{\exists x\neg A(x)})\to P_\varphi,  (P_{\neg \forall xA(x)}\wedge P_{\forall xA(x)})\to\bot\}\\&\cup\{P_{\forall xA(x)}\to \forall xP_{A(x)}(x), \forall x(A(x)\to P_{A(x)}(x))\}\\&\cup\{\exists xP_{\neg A(x)}(x)\to P_{\exists x\neg A(x)}, \forall x((P_{A(x)}(x)\to \bot)\to P_{\neg A(x)}(x))\}\\&\cup\{\forall x(P_{A(a)}(x)\to A(x))\}
	\end{align*}
\end{example}

We can give a transformation of structures that corresponds to the above transformation of sentences.

\begin{definition}
	For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms of the form $P_\psi$. By slight abuse of notation we denote with $\vec z_\psi$ elements of the domain instead of variables. In the classical case have
	$$P_A^I(\vec z_A):\Leftrightarrow A^I(\vec z_A)$$
	and
	$$P_{\varphi\wedge\psi}^I(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\wedge P_{\psi}^I(\vec z_\psi)\indent P_{\varphi\vee\psi}^I(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\vee P_{\psi}^I((\vec z_\psi))$$$$ P_{\varphi\to\psi}^I(\vec z_{\varphi\to\psi}) :\Leftrightarrow (\neg P_{\varphi}^I(\vec z_{\varphi}))\vee P_{\psi}^I(\vec z_{\psi})$$
	$$P_{\forall x\varphi}^I(\vec z_{\forall x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for all $x\in M$}\}$$$$ P_{\exists x\varphi}^I(\vec z_{\exists x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for some $x\in M$}\}$$
	\\
	and for intuitionistic logic and some world $u$
	$$P_A^{I_u}(\vec z_A):\Leftrightarrow A^{I_u}(\vec z_A)$$
	and
	$$P_{\varphi\wedge\psi}^{I_u}(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\wedge P_{\psi}^{I_u}(\vec z_\psi)\indent P_{\varphi\vee\psi}^{I_u}(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\vee P_{\psi}^{I_u}((\vec z_\psi))$$$$ P_{\varphi\to\psi}^{I_u}(\vec z_{\varphi\to\psi}) :\Leftrightarrow(\neg P_{\varphi}^{I_w}(\vec z_{\varphi}))\vee P_{\psi}^{I_w}(\vec z_{\psi})\text{ for all $w\geq u$}$$
	$$P_{\forall x\varphi}^{I_u}(\vec z_{\forall x\varphi}) :\Leftrightarrow P_{\varphi}^{I_w}(\vec z_\varphi) \text{ for all $w\geq u$, $x\in M_w$}$$$$ P_{\exists x\varphi}^{I_u}(\vec z_{\exists x\varphi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi) \text{ for some $x\in M_u$}$$
	\\
\end{definition}

@@

\begin{lemma}
	For every formula $\varphi$ and structure $\mathcal M$
	$$\mathcal S(\mathcal M, \varphi)\models\mathcal S^+(\varphi)\cup S^-(\varphi)$$
\end{lemma}

\begin{lemma}
	For every structure $\mathcal M$
	$$\mathcal M\models \varphi\text{ iff }S(\mathcal M, \varphi)\models P_\varphi$$
\end{lemma}

@@

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$$
where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u),$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))$$
$$\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l))\to C(k)))$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k))), \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))$$
$$\hspace*{-2mm}\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k))), \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))$$
$$\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k)),$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $$M' = \{m\in M|s\preceq m\}$$ and
$$f_\psi^{I'}(u) = \begin{cases}
	f^I_\psi(u), &\text{ iff $u\preceq f^{I}_\psi(u)$,}\\
	u,&\text{ else.}
\end{cases}$$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\forall k(A(k)\to (B(k)\wedge C(k))), \forall k((A(k)\wedge B(k))\to C(k))$$
$$\forall k(A(k)\to (B(k)\vee C(k))), \forall k((A(k)\vee B_\psi(k))\to C(k))$$
$$\forall k((A(f_\psi(k))\to B(f_\psi(k)))\to C(k))$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

\begin{corollary}
	If $\mathcal M$ is a counter-model to $\varphi^\circ$ then so is $\mathcal M_T$.
\end{corollary}

>>>>

\usepackage{wrapfig}
\usepackage{tikz-qtree}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{arrows,shapes,quotes}

@@

\begin{theorem}\label{thm:prop-translation}
	Let $\mathcal S$ be as above. Let $\mathcal F_\to\subseteq\mathcal S$ denote formulas $\psi$ of the form $(A_\psi\to B_\psi)\to C_\psi$ and $\Lambda$ denote the set of sequences without repetition over $\mathcal F_\to$. For each atom $A$ and $k\in\Lambda$ consider a new atom $A^k$. Obtain $\mathcal S^\#$ by including formulas as follows
	\begin{itemize}
		\item $A^k\to A^{k\psi}$ for each atom $A$ occurring in $\mathcal S$, $k\in\Lambda$ and $\psi\in\mathcal F_\to$ not occurring in $k$.
		\item $A^k\to (B^k\circ C^k)$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^k\circ B^k)\to C^k$ for each $\circ\in\{\wedge,\vee\}$, $A\to (B\circ C)\in\mathcal S$, $k\in\Lambda$.
		\item $(A^{k\psi}\to B^{k\psi})\to C^k$ for $\psi = (A\to B)\to C\in\mathcal S$, $k\in\Lambda$ if $\psi$ does not occurr in $k$.
	\end{itemize}
	Then $\bigwedge S\to P$ is intuitionistically valid iff $\bigwedge S^\#\to P^\epsilon$ is classically valid, where $\epsilon$ denotes the empty sequence. The size of $\mathcal S^\#$ is in $\mathcal O(|\mathcal S|\cdot2^{|\mathcal F_\to|\cdot\log(|\mathcal F_\to|)})$. Futhermore there is an effective procedure for translating counter-models between the sentences.
\end{theorem}

@@

\begin{theorem}
	For every predicate formula $\varphi$ there exists an effective procedure that yields an atom $P$ and a set $\mathcal S$ of formulas of the forms
	$$\begin{matrix}
		\forall \vec z(A(\vec a)\to (B(\vec b)\wedge C(\vec c))), \forall \vec z((A(\vec a)\wedge B(\vec b))\to C(\vec c)),\forall \vec z(A(\vec a)\to (B(\vec b)\vee C(\vec c))),\\
		\forall \vec z((A(\vec a)\vee B(\vec b))\to C(\vec c)), \forall \vec z((A(\vec a)\to B(\vec b))\to C(\vec c)),\forall \vec z(\forall xA(\vec a)\to B(\vec b)),\\ \forall \vec z(A(\vec a)\to\forall xB(b)), \forall \vec z(\exists xA(\vec a)\to B(\vec b)), \forall \vec z(A(\vec a)\to\exists xB(b))
	\end{matrix}$$
	for atomic $A, B, C$ and vectors of variables $\vec z, \vec a, \vec b, \vec c$ such that $\varphi$ is intuitionistically valid if and only if $\bigwedge\mathcal S\to P$ is intuitionistically valid. The size of $\mathcal S$ and time complexity of the transformation are linear in the input size.
\end{theorem}

@@

\begin{definition}
A \emph{valuation} $v$ maps each propositional variable $A$ to a \emph{truth value} $v(A)\in\{0, 1\}$. We inductively define the model relation $\models$ between $v$ and formulas:
	\begin{itemize}
		\item $v\not\models \bot$ and $v\models A$ iff $v(A) = 1$ for each propositional variable $A$.
		\item $v\models \varphi\wedge\psi$ iff $v\models\varphi$ and $v\models\psi$.
		\item $v\models\varphi\vee\psi$ iff $v\models\varphi$ or $v\models\psi$.
		\item $v\models\varphi\to \psi$ iff $v\not\models\varphi$ or $v\models\psi$.
	\end{itemize}
A valuation $v$ is a \emph{model} for $\varphi$ if $v\models\varphi$. If every valuation is a model for $\varphi$ then we say $\varphi$ is \emph{valid}. We denote the set of valid formulas with \emph{CPC} (Classical Propositional Calculus).
\end{definition}

@@

\begin{definition}
Let $\Sigma$ be a signature. A $\Sigma$-structure $\mathcal{M}$ consists of a non-empty set $M$, the \emph{domain} of $\mathcal{M}$, and an \emph{interpretation} $I$ that assigns
	\begin{itemize}
		\item to each $n$-ary function symbol $f$ a $n$-ary function $f^I: M^n\to M$.
		\item to each $n$-ary relation symbol $R$ a $n$-ary relation $R^I\subseteq M^n$.
	\end{itemize}
	A variable assignment $v$ is a function that assigns to each free variable an element $m\in M$. For each free variable $a$ and $m\in M$ we define $$v[m/a](b) = \begin{cases}
		m, &\text{if $b=a$,}\\
		v(b), &\text{otherwise.}
	\end{cases}$$
	Then terms are interpreted as follows:
	\begin{itemize}
		\item $a^{I, v} = v(a)$ for each free variable $a$.
		\item $f(t_1,\dots,t_n)^{I, v} = f^I(t_1^{I, v},\dots, t_n^{I, v})$.
	\end{itemize}
	We define a model relation between pairs $\mathcal M, v$ and formulas $\varphi$ as follows
	\begin{itemize}
		\item $\mathcal M, v\not\models\bot$ and  $\mathcal M, v\models R(t_1,\dots,t_n)$ iff $(t_1^{I, v},\dots,t_n^{I, v})\in R^I$.
		\item $\mathcal M, v\models s = t$ iff $s^{I, v} = t^{I, v}$.
		\item $\mathcal M, v\models \varphi\wedge \psi$ iff $\mathcal M, v\models\varphi$ and $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\vee\psi$ iff $\mathcal M, v\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models \varphi\to\psi$ iff $\mathcal M, v\not\models\varphi$ or $\mathcal M, v\models\psi$.
		\item $\mathcal M, v\models\exists x\varphi$ iff there exists $m\in M$ such that $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $\mathcal M, v\models\forall x\varphi$ iff for all $m\in M$ we have $\mathcal M, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{M}$ satisfies $\varphi$ if $\mathcal M, v\models\varphi$ for every $v$. A formula is valid if every $\Sigma$-structure satisfies it. We denote the set of valid formulas with \emph{CQC} (Classical Quantified Calculus).
\end{definition}

\begin{definition}
	A $\Sigma$-\emph{Kripke structure} $\mathcal{K}$ is a partially ordered set $W$, its (Kripke) \emph{Frame}, and a family of $\Sigma$-structures $(\mathcal{M}_w)_{w\in W}$ such that for $u\leq w$
	\begin{itemize}
		\item $M_u\subseteq M_w$.
		\item $f^{I_w}|_{M_u} = f^{I_u}$.\footnote{Here $f|_M$ denotes the restriction of $f$ to $M$}
		\item $R^{I_w}|_{M_u} = R^{I_u}$.
	\end{itemize}
	Then we define a model relation between worlds $u\in W$ and variable assignments $v$ (targeting $M_u$) and formulas $\varphi$ as follows:
	\begin{itemize}
		\item $u, v\not\models\bot$ and $u, v\models R(t_1,\dots,t_n)$ iff $\mathcal M_u, v\models R(t_1,\dots,t_n)$.
		\item $u, v\models s = t$ iff $s^{I_u, v} = t^{I_u, v}$.
		\item $u, v\models \varphi\wedge \psi$ iff $u, v\models\varphi$ and $u, v\models\psi$.
		\item $u, v\models \varphi\vee\psi$ iff $u, v\models\varphi$ or $u, v\models\psi$.
		\item $u, v\models \varphi\to\psi$ iff for every $w\geq u$ we have $w, v\not\models\varphi$ or $w, v\models\psi$.
		\item $u, v\models\exists x\varphi$ iff there exists $m\in M_u$ such that $u, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
		\item $u, v\models\forall x\varphi$ iff for every $w\geq u$ and $m\in M_w$ we have $w, v[m/a]\models\varphi[a/x]$ where a is a free variable that does not occur in $\varphi$.
	\end{itemize}
	$\mathcal{K}$ satisfies $\varphi$ if $u, v\models\varphi$ holds for every world $u$ and variable assignment $v$. A formula is valid if it is satisfied in eveery $\Sigma$-Kripke structure, it is valid for some Frame (write $W\models\varphi$) if it is satisfied in every Krike structure with that Frame. We denote the set of valid formulas with \emph{IQC} (Intuitionistic Quantified Calculus).
\end{definition}
In addition to the propositional tautologies there are now sentences involving quantifiers which are classically valid but not intuitionistically, e.g., $\neg\forall x A(x)\to \exists x \neg A(x)$.
Analogous remarks with regard to validity and satisfiability hold as in the propositional case.

@@

@@

\begin{lemma}
	$\bigwedge S^+(\varphi)\wedge P_\varphi\to\varphi$, $\bigwedge S^-(\varphi)\wedge \varphi\to P_\varphi$ hold classically and intuitionistically.
\end{lemma}

We give a transformation of structures that corresponds to the above.

\begin{definition}
	For every classical and intuitionistic structure $\mathcal M$ define a structure $\mathcal S(\mathcal M,\varphi)$ that agrees with $\mathcal M$ on everything except the interpretation(s) of atoms of the form $P_\psi$. By slight abuse of notation we denote with $\vec z_\psi$ elements of the domain instead of variables. In the classical case have
	$$\begin{matrix}
		P_A^I(\vec z_A):\Leftrightarrow A^I(\vec z_A)\indent P_{\varphi\wedge\psi}^I(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\wedge P_{\psi}^I(\vec z_\psi)\indent P_{\varphi\vee\psi}^I(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^I(\vec z_\varphi)\vee P_{\psi}^I((\vec z_\psi))\\P_{\varphi\to\psi}^I(\vec z_{\varphi\to\psi}) :\Leftrightarrow (\neg P_{\varphi}^I(\vec z_{\varphi}))\vee P_{\psi}^I(\vec z_{\psi})\\P_{\forall x\varphi}^I(\vec z_{\forall x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for all $x\in M$}\}\indent P_{\exists x\varphi}^I(\vec z_{\exists x\varphi}) :\Leftrightarrow \{\vec z\:|\:\:P_{\varphi}^I(\vec z_\varphi) \text{ for some $x\in M$}\}
	\end{matrix}$$
	and for intuitionistic logic and each world $u$
	$$\begin{matrix}
		P_A^{I_u}(\vec z_A):\Leftrightarrow A^{I_u}(\vec z_A)\indent P_{\varphi\wedge\psi}^{I_u}(\vec z_{\varphi\wedge\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\wedge P_{\psi}^{I_u}(\vec z_\psi)\indent P_{\varphi\vee\psi}^{I_u}(\vec z_{\varphi\vee\psi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi)\vee P_{\psi}^{I_u}((\vec z_\psi))\\
		 P_{\varphi\to\psi}^{I_u}(\vec z_{\varphi\to\psi}) :\Leftrightarrow(\neg P_{\varphi}^{I_w}(\vec z_{\varphi}))\vee P_{\psi}^{I_w}(\vec z_{\psi})\text{ for all $w\geq u$}\\
		 P_{\forall x\varphi}^{I_u}(\vec z_{\forall x\varphi}) :\Leftrightarrow P_{\varphi}^{I_w}(\vec z_\varphi) \text{ for all $w\geq u$, $x\in M_w$}\indent P_{\exists x\varphi}^{I_u}(\vec z_{\exists x\varphi}) :\Leftrightarrow P_{\varphi}^{I_u}(\vec z_\varphi) \text{ for some $x\in M_u$}
	\end{matrix}$$
\end{definition}

@@

\begin{lemma}
	For every formula $\varphi$ and structure $\mathcal M$
	$\mathcal S(\mathcal M, \varphi)\models\mathcal S^+(\varphi)\cup S^-(\varphi)$
\end{lemma}

\begin{lemma}
	For every structure $\mathcal M$
	$\mathcal M\models \varphi$ if and only if $S(\mathcal M, \varphi)\models P_\varphi$
\end{lemma}

@@

Recall that since $\varphi$ is quantifier-free each formula $\psi\in\mathcal S^-(\varphi)$ is of one of the forms
$$A\to (B\wedge C), (A\wedge B)\to C, A\to (B\vee C), (A\vee B)\to C, (A\to B)\to C,$$
where we can treat $A\to B$ as a special case $A\to (B\wedge B)$. We then apply the transformation to CQC, leading to a formula
$$\varphi'' = K(\varphi')\to\bigwedge  \mathcal S\to P_\varphi(u),$$
where $u$ is some new free variable and each $\psi\in\mathcal S$ is of one of the forms
$$\begin{matrix}
	\forall k(u\preceq k\to A(k)\to (B(k)\wedge C(k)))\indent  \forall k(u\preceq k\to (A(k)\wedge (B(k))\to C(k)))\\
	\forall k(u\preceq k\to A(k)\to (B(k)\vee C(k)))\indent \forall k(u\preceq k\to (A(k)\vee B(k))\to C(k))\\
	\forall k(u\preceq k\to (\forall l(k\preceq l \to A(l)\to B(l))\to C(k)))
\end{matrix}$$
with each $P(x)$ possibly being $\bot$. Applying Herbrandization we obtain a formula
$$\varphi''' = K(\varphi')\to \bigwedge \mathcal S'\to P_\varphi(s)$$
where $s$ is some new constant term and each $\psi\in\mathcal S'$ is of one of the forms
$$\begin{matrix}
	\forall k(s\preceq k\to A(k)\to (B(k)\wedge C(k)))\indent \forall k(s\preceq k\to (A(k)\wedge (B(k))\to C(k)))\\
	\forall k(s\preceq k\to A(k)\to (B(k)\vee C(k)))\indent \forall k(s\preceq k\to (A(k)\vee (B(k))\to C(k)))\\
	\forall k(s\preceq k\to (k\preceq f_\psi(k) \to A(f_\psi(k))\to B(f_\psi(k)))\to C(k))\\
\end{matrix}$$
and $f_\psi$ is a new function symbol for each introduced formula of that form. Now if $(M, I)$ is a counter-model then we have a counter-model $(M',I')$ where $M' = \{m\in M|s\preceq m\}$ and
$f_\psi^{I'}(u) = f^I_\psi(u) \text{ iff $u\preceq f^{I}_\psi(u)$ and $f_\psi^{I'}(u) = u$ else.}$ that is where $s$ is a least element and the $f_\psi$ increase their argument. Therefore instead of $\varphi'''$ we may consider a formula $$\varphi^\circ = \forall k(s\preceq k)\to \bigwedge\{\forall k(k\preceq f_\psi(k))\:|\:\psi\in\mathcal F_\to\}\to K(\varphi')\to \bigwedge \mathcal S^\circ\to P_\varphi(s)$$ where each formula $\psi\in\mathcal S^\circ$ is of one of the forms
$$\begin{matrix}
	\forall k(A(k)\to (B(k)\wedge C(k)))\indent\forall k((A(k)\wedge B(k))\to C(k))\\
	\forall k(A(k)\to (B(k)\vee C(k)))\indent\forall k((A(k)\vee B_\psi(k))\to C(k))\\
	\forall k((A(f_\psi(k))\to B(f_\psi(k)))\to C(k))
\end{matrix}$$
and $\mathcal F_\to$ denotes the set of formulas of the last kind.

@@

\begin{corollary}\label{cor:prop-tree-model}
	If $\mathcal M$ is a counter-model to $\varphi^\circ$ then so is $\mathcal M_T$.
\end{corollary}

An examples of this translation can be found in the appendix.
